A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-29 paper/ms.tex
update ms

\citet{kounkel_untangling_2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.},
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be significantly
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

@@

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is significantly larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

@@

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and a white noise 
jitter ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not significantly affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano},
and accounted for the finite integration time of each exposure in the
numerical integration when evaluating the model light curve
\citep[see][]{kipping_binning_2010}.  We assumed a Gaussian
likelihood, and after initializing each model with the parameters of
the maximum {\it a posteriori} model, we sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in the bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

@@

The expectation however is for the starspot-induced signals to be smooth,
at worst with contributions at $0.5\,P_{\rm rot}$ or $0.25\,P_{\rm
rot}$ \citep{klein_simulated_2020}.  We therefore fitted the RVs using
the \citet{hirano_analytic_2010,hirano_2011} models for the
Rossiter-McLaughlin (RM) effect, and allowed for an optional linear
and quadratic trend in time to fit the 800\ms\ spot-induced trend.  We
followed the methodology developed by \citet{stefansson_2020}.  We
allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary,
and fixed the limb-darkening using the $V$-band tabulation from
\citet{claret_gravity_2011}.  We assumed a prior on $v\sin i$ and
$a/R_\star$ from Table~\ref{tab:starparams}, and also allowed for a
white-noise jitter term to be added in quadrature to the measurement
uncertainties.

@@

The amplitude of both the spot-induced trend and the jitter are larger
than recent comparable measurements in systems such as AU~Mic
\citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates the measurement
uncertainties; the S/N per resolution element for each of our spectra
was moderated by the observing requirements to 70 to 80, and the rapid
rotation of the star could affect accuracy of the uncertainties from
the velocity extraction.  Observations at higher precision are
necessary to distinguish these two possibilities, and remain
worthwhile as a means toward clarifying the orbital geometry of \pn.

>>>>

\citet{kounkel_untangling_2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.},
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be heavily
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

@@

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

@@

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and a white noise 
jitter ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano},
and accounted for the finite integration time of each exposure in the
numerical integration when evaluating the model light curve
\citep[see][]{kipping_binning_2010}.  We assumed a Gaussian
likelihood, and after initializing each model with the parameters of
the maximum {\it a posteriori} model, we sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in the bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

@@

The expectation however is for the starspot-induced signals to be smooth,
at worst with contributions at $0.5\,P_{\rm rot}$ or $0.25\,P_{\rm
rot}$ \citep{klein_simulated_2020}.  We therefore fitted the RVs using
the \citet{hirano_analytic_2010,hirano_2011} models for the
Rossiter-McLaughlin (RM) effect, and allowed for an optional linear
and quadratic trend in time to fit the 800\ms\ spot-induced trend.  We
followed the methodology developed by \citet{stefansson_2020}.  We
allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary,
and fixed the limb-darkening using the $V$-band tabulation from
\citet{claret_gravity_2011}.  We assumed a Gaussian prior on $v\sin i$ and
$a/R_\star$ from Table~\ref{tab:starparams}, and also allowed for a
white-noise jitter term to be added in quadrature to the measurement
uncertainties.

@@

The amplitude of both the spot-induced trend and the jitter are larger
than recent comparable measurements in systems such as AU~Mic
\citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates our measurement
uncertainties; the S/N per resolution element for each of our spectra
was 70 to 80, which is somewhat low for deriving high-precision
velocities.  In addition, the rapid rotation of the star could affect
accuracy of the uncertainties from the velocity extraction.
Observations at higher precision are necessary to distinguish these
two possibilities, and remain worthwhile as a means toward clarifying
the orbital geometry of \pn.
